% Preamble
\input{preamble}

\begin{document}
\pagestyle{fancy}
\input{bom-table}
\newpage

\begin{newmargin}{0.5in}
    \section*{Important Notice and Disclaimer}
    The information contained in this document is provided exclusively for your convenience. These resources are subject to change without notice. Theta Machines LLC disclaims all liability arising from the information contained herein and its use. You are solely responsible for (1) designing and thoroughly testing your solution and (2) ensuring your solution meets applicable standards and requirements. 

    This work is licensed under a Creative Commons Attribution-ShareAlike 4.0 International License. A copy of this license can be found at \url{https://creativecommons.org/licenses/by-sa/4.0/}. No license is granted to any other intellectual property right held by Theta Machines LLC or third parties.
    
    \section*{Trademarks}
    All trademarks are the property of their respective owners.
    
    All company, brand, and product names used in this document are for identification purposes only. Use of these names does not imply affiliation with the respective owners.

    \section*{Document Version History}
    % Column width scale factors (\hsize=) must all add up to 1
    \begin{tabularx}{\linewidth}{| >{\hsize=0.1\hsize}X | >{\hsize=0.2\hsize}X | >{\hsize=0.7\hsize}X |}
        \hline
        \rowcolor{lightgray!50} 
        \textbf{Version} &
        \textbf{Date} &
        \textbf{Changes} \\
        \hline
        1.0 & \today & Initial release \\
        \hline
    \end{tabularx}

    \vspace{0.5\baselineskip}
    \section*{Suggest Changes}
    Have a suggestion? Found an error? Let us know by opening an issue on GitHub (\url{https://github.com/theta-machines/theta-docs/issues}) or contacting us at \href{mailto:support@thetamachines.com}{support@thetamachines.com}.

\end{newmargin}
\end{document}
